%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}

% \titlespacing{\section}{0pt}{50pt}{10pt}
% \setlist{}
% \setlength{}

\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item{
		\vspace{-2pt}
    	\textbf{#1: \\}
		\vspace{-2pt} 
		\begin{itemize} 
            #2
		\end{itemize}
	}
}

\newcommand{\resumeItemDetail}[1]
{
    \item \small{ #1 \vspace{-2pt} }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeEducation}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
	  % \hspace{5pt} \textit{\small#5}\\ % GPA
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumePublication}[3]{
    \vspace{-1pt}
    \item{
        \vspace{-2pt}
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
            \textbf{#1} & #2 \\
        \end{tabular*}\vspace{-5pt}
        \vspace{-2pt}
        \begin{itemize} 
            \vspace{-2pt}
                #3
        \end{itemize}\vspace{-10pt}
    }
}

\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[label={},leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeSubheadingList}[1]
{
    \begin{itemize}[label={},leftmargin=*]
        #1
    \end{itemize}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeItemList}[1]
{
    \begin{itemize}
        #1
    \end{itemize}\vspace{-5pt}
}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%



\begin{document}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    {\Large Ting-Hsiang Wang} & Email : \href{mailto:thwang1231@gmail.com}{thwang1231@gmail.com}\\
    & Mobile : +886 988-089-724
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubheadingList
  {
	\resumeEducation
      {University of Illinois at Urbana-Champaign}{Illinois, USA}
	  {Bachelor of Science in Mathematics and Computer Science}{Fall 2008 - Fall 2013}
	  % {Overall GPA$:$ $2.79/4.00$}
  }

%-----------PUBLICATION-----------------
\section{Publication}
\resumeSubheadingList
{
    \resumePublication{ICE: Item Concept Embedding via Textual Information}{SIGIR 2017}
    {
        \resumeItemDetail{Accepted to the 40th International ACM SIGIR Conference as a regular paper.}
    }
    \resumePublication{Superhighway: Bypass Data Sparsity in Cross-Domain Collaborative Filtering}{RecSys 2018}
    {
        \resumeItemDetail{Accepted to the 12th ACM Conference on Recommender Systems as a poster paper.}
    }
    \resumePublication{Item Concept Network: Towards Concept-based Item Representation Learning}{Submitted}
    {
		\resumeItemDetail{Submitted to the IEEE Transactions on Knowledge and Data Engineering as a journal paper.}
    }
}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Academia Sinica}{Taipei, Taiwan (R.O.C)}
      {Research Assistant}{Aug. 2017 - Present}
      \resumeItemListStart
        \resumeItem{Research on Network Embedding}
        {
		    \resumeItemDetail{Collaboratively developed network embedding framework (proNet) which was released on the github for large-scale network embedding and simulation of different kinds of embedding algorithm including matrix-factorization based methods, random walk based methods, SkipGram based methods...etc.}
		    \resumeItemDetail{Developed a factorization based method to modeling user sequential behavior for user clustering analysis.}
		    \resumeItemDetail{Developed random walk based network embedding methods for building various kinds of recommender systems.}
        }
      \resumeItemListEnd
    \resumeSubheading
      {KKBOX Taiwan Co.,Ltd}{Taipei, Taiwan (R.O.C)}
      {Data Researcher Intern}{Apr. 2017 - Present}
      \resumeItemListStart
        \resumeItem{Recommendation System Development}
        {
            \resumeItemDetail{Developed a random-walk based representation learning model for recommendation system}
            \resumeItemDetail{Developed a centrality based sample strategy for random walk based representation learning model with dynamic walking length, walking style and sample times.}
            \resumeItemDetail{Developed a network construction algorithm with random-walk based network embedding algorithm for cross-market recommendation which doubled the offline performance of recommender system.}
        }
      \resumeItemListEnd
    \resumeSubheading
      {Cathay United Bank}{Taipei, Taiwan (R.O.C)}
      {Data Researcher Intern}{Aug. 2017 - Present}
      \resumeItemListStart
        \resumeItem{Customer Journey Modeling}
        {
            \resumeItemDetail{Analyzed transaction records up to 2017 from 5 kinds of channels to the scale of 10TB via data visualization with Elastic Search.}
		    \resumeItemDetail{Processed customer journey data and extracted critical features based on the analysis.}
		    \resumeItemDetail{Utilized gradient boosting tree model to build a ranking-based decision model for credit card customer churn prediction.}
		    \resumeItemDetail{Developed a end-to-end system for rapid deployment for non-technical personnels in data analysis on customer journey data.}
            \resumeItemDetail{Developed a large-scale learning algorithm for modeling users' sequential behavior which facilitated 10\% enhancement in terms of AUC for customer churn prediction.}
        }
      \resumeItemListEnd
    \resumeSubheading
      {R.O.C Army Aviation and Special Forces Command}{Taoyuan, Taiwan (R.O.C)}
      {Paratrooper}{Sept. 2015 - Sept. 2016}
      \resumeItemListStart
        \resumeItem{Receiving Foreign Ambassadors}
        {
            \resumeItemDetail{Welcomed the foreign ambassadors with our president.}
        }
        \resumeItem{Perform Drill Show in National Celebration}
        {
		    \resumeItemDetail{Performed drill show on national celebration days such as national day, new year's day and presidential inauguration.}
        }
        \resumeItem{Guarding National Revolutionary Martyr's Shrine}
        {
		    \resumeItemDetail{Guarded martyr's shrine to honor the great people in our country.}
        }
      \resumeItemListEnd

    \resumeSubheading
      {LEADERG Inc.}{Taipei, Taiwan (R.O.C)}
      {Software Engineer Intern}{Jul. 2014 - Apr. 2015}
      \resumeItemListStart
        \resumeItem{Online Prototyping Platform}
        {
          \resumeItemDetail{Developed an online prototyping tool, solved problem of curvature rendering latency on web based platform by developing a asynchronous strategy for mesh rendering in different resolution and precisely calculation by A/B test.}
        }
        \resumeItem{Cloud Drive}
        {
		    \resumeItemDetail{Developed a personal Cloud Drive device's user interface for accessing the device directly, and integrated with online cloud drive such as google drive and dropbox.}
		    \resumeItemDetail{Designed a database structure for interaction between device users data sharing scheme and simulating social network. }
        }
        \resumeItem{Web Development}
        {
		  \resumeItemDetail{Integrated front-end and back-end of websites including various function such as online payment, shopping cart, profile management, newsletter subscription.}	
        }
      \resumeItemListEnd
	\resumeSubHeadingListEnd

%-----------Open Source Project-----------------
\section{Open Source Project}
  \resumeSubHeadingListStart
    \resumeItem{proNet-Core}
    {
          \resumeItemDetail{ \href{https://github.com/cnclabs/proNet-core}{https://github.com/cnclabs/proNet-core}}
          \resumeItemDetail{Implemented state-of-the-art network embedding algorithms including LINE, DeepWalk, etc.}
          \resumeItemDetail{Developed the function of loading pre-train model for further research on online learning.}
    }
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Selected Course Project}
  \resumeSubHeadingListStart
    \resumeItem{Special Topics on Computer Science(95/100) - Novel Remaking Prediction}
    {
        {Built a crawler for crawling movies and novels data from Amazon and IMDb. (Around 14GB)}
	    {Performed text processing, including parsing, segmentation and tokenization for sentiment analysis}
	    {Trained a binary classifier via support vector machine by processed features and ground truths for predicting novel remaking.}
    }
  \resumeSubHeadingListEnd

%%-----------ACHIEVEMENT-----------------
%\section{Achievement}
%  \resumeSubHeadingListStart
%	\resumeSubheading
%		{NASA Space App Hackthon}{Taiwan (R.O.C)}
%		{Judges' list Award}{Apr. 2017}
%	\resumeSubheading
%		{Taiwan Hackthon 4th}{Taiwan (R.O.C)}
%		{Best Popularity Award}{Feb. 2015}
%	\resumeSubheading
%		{Living Lab Testing Service Awards}{Taiwan (R.O.C)}
%		{1st Place Award}{Jan. 2014}
%  \resumeSubHeadingListEnd
\section{Activities}
  \resumeSubHeadingListStart
	\resumeSubheading
		{Taiwan Data Science Foundation}{Taiwan (R.O.C)}
		{Volunteer}{Nov. 2017}
      \resumeItemListStart
		\resumeItem{Taiwan Artificial Intelligence and Data Science Conference}
        {
		    \resumeItemDetail{Managed conference provisions and logistics.}
		    \resumeItemDetail{Designed and arranged the layout of reception area.}
        }
      \resumeItemListEnd
%	\resumeSubheading
%		{Waker Organization}{Nepal}
%		{Voluntary Teacher}{Aug.-Sept. 2014}
%      \resumeItemListStart
%        \resumeItem{Courses of science and technologies}
%          {Designed and taught a series of courses related to science and technologies including mathematics, physics and chemistry for children in Nepal.}
%      \resumeItemListEnd
    \resumeSubheading
      {Student Association of department of computer science}{Taipei, Taiwan (R.O.C)}
      {Director of Department of Activity Organization}{Sept. 2012 - Sept. 2014}
      \resumeItemListStart
        \resumeItem{Orientation Camp}
        {
            \resumeItemDetail{Coordinates students from other departments for the union orientation camp for freshman.}
		    \resumeItemDetail{Led a 100 people scaled group to organize the orientation camp for freshman from two departments.}
        }
		\resumeItem{Computer Science Summer Camp}
        {
		    \resumeItemDetail{Led a 100 people scaled group to organize the computer science camp for high school students.}
		    \resumeItemDetail{Designed the process of activities and the content of courses related to computer science for the summer camp.}
        }
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%%%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C++, Python, Java, Javascript, Bash Script, PHP, HTML, CSS}
	}
	\item{
      \textbf{Technologies}{:  Network Embedding, Recommendation System, Natural Language Processing, Information Retrieval, AWS, IBM Bluemix, Web Application}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
